The Bolocam Galactic Plane Survey: Survey Description and Data Reduction

### 2009-04-17 methods/ms.tex
distmaps

The absolute pointing accuracy of the survey has been measured to be
$\sim$6\arcsec\ RMS (figure \ref{fig:PointingModel}.  A single $3^\circ \times
1^\circ$ observation of each region was registered to the pointing calibrators
as a ``master field'', and additional observations of that field were aligned
to the master (Section \ref{sec:Astrometry}).

>>>>

The absolute pointing accuracy of the survey has been measured to be
$\sim$6\arcsec\ RMS (figure \ref{fig:PointingModel}.  The Epoch V pointing model
was used to make pointing reference fields which were then median combined
using IRAF to make a higher S/N reference field with somewhat reduced pointing
errors (Section \ref{sec:Astrometry}).

% A single $3^\circ \times
% 1^\circ$ observation of each region was registered to the pointing calibrators
% as a ``master field'', and additional observations of that field were aligned
% to the master (Section \ref{sec:Astrometry}).
